Title

### 2013-03-18 inc/laser/laser.tex
introduction to hardware is now its own file
tweaked laser intro

\section{Yb:KGW Laser System} \label{sec:laser}
\subsection{Introduction}
% Draws from:
% High-power, femtosecond, thermal-lens-shaped Yb:KGW oscillator
% Joel A. Berger, Michael J. Greco, and W. Andreas Schroeder
% 9 June 2008 / Vol. 16, No. 12 / OPTICS EXPRESS

% page 8630
Ytterbium-doped potassium gadolinium tungstate (\ce{Yb$:$KGd(WO4)2} or Yb:KGW) is becoming a widely used solid-state gain medium for ultrafast laser systems.
As with other Yb-doped laser crystals \cite{Brenier_new_criteria}, this is primarily due to the gain medium's advantageous absorption properties for direct laser diode pumping at 980nm, its broad emission bandwidth around 1040nm, and consequent small ($\sim$ 6\%) quantum defect that results in a relatively low thermal load. 
Mode-locked (ML), diode-pumped, Yb:KGW laser oscillators generating pulses with sub-picosecond durations at average output powers in excess of 1W have been demonstrated \cite{Brunner_diode_pumped,Courjaud_high_power,Major_femtosecond_2006,Holtom_mode_locked_2006} and are now available commercially \cite{website_amplitude,website_solar}.
Such lasers have used dichroic mirrors \cite{Brunner_diode_pumped,Major_femtosecond_2006,Paunescu_diode_2004,Major_extended_2006}, polarization-coupling \cite{Holtom_mode_locked_2006}, or more complex optical geometries (e.g., thin disk lasers \cite{website_amplitude,Brunner_pulses_2002}) to pump the laser crystal in an efficient manner.

@@

%TODO is this first sentance correct or should I use "I" voice?
In this section, a high-power, femtosecond Yb:KGW oscillator is presented that also accesses the broader emission bandwidth parallel to the optical $N_p$-axis (parallel to the crystallographic $b$-axis), yet employs a simpler geometry for polarized diode-pumping on the strongest 980nm absorption line parallel to the optical $N_m$-axis (rotated by $\sim\,20^\circ$ from the crystallographic $a$-axis \cite{Biswal_thermo_optical_05,mochalov_laser_1997,pujol_crystalline_1999}).
The laser head design is based on the thermal lens shaping (TLS) technique developed in-house for astigmatism compensation in diode-pumped Nd-doped lasers with Brewster-cut gain media \cite{Rimington_thermal_lens_2004}.
It employs a simple single layer \ce{SiO2} anti-reflection coating on the gain medium to provide minimal loss for $p$-polarized intracavity 1040nm laser radiation and less than 0.5\% surface reflection for orthogonal $s$-polarized 980nm pump light.
The result is a simple and robust, soliton mode-locked and directly diode-pumped, solid-state laser oscillator delivering over 4W of average output power in a 63MHz train of pulses with a duration less than 300fs.
Frequency doubling of this laser output in a 2mm Brewster-cut Lithium triborate (LBO) crystal provides 1.65W of average power at 520nm.

>>>>

\section{Yb:KGW Laser System} \label{sec:laser}

% Draws from:
% High-power, femtosecond, thermal-lens-shaped Yb:KGW oscillator
% Joel A. Berger, Michael J. Greco, and W. Andreas Schroeder
% 9 June 2008 / Vol. 16, No. 12 / OPTICS EXPRESS

In order to experiment using very short laser pulses, we have designed and built a custom Ytterbium-doped potassium gadolinium tungstate (\ce{Yb$:$KGd(WO4)2} or Yb:KGW) laser system.\cite{berger_high-power_2008}
In practice, the flexibility afforded by having a custom-built system has outweighed its original performance benefit.
I have shown in Section \ref{sec:initial_conditions} that the electron pulse duration is not a simple function of the laser pulse duration, yet, at the time the laser was built, this fact was not yet obvious.
As such, our laser was designed to produce relatively high power output while generating ultrashort pulses, on the order of 250 fs for some conditions.

\subsection{Laser Introduction}
% page 8630
Yb:KGW is becoming a widely used solid-state gain medium for ultrafast laser systems.
As with other Yb-doped laser crystals \cite{Brenier_new_criteria}, this is primarily due to the gain medium's advantageous absorption properties for direct laser diode pumping at 980nm, its broad emission bandwidth around 1040nm, and consequent small ($\sim$ 6\%) quantum defect that results in a relatively low thermal load. 
Mode-locked (ML), diode-pumped, Yb:KGW laser oscillators generating pulses with sub-picosecond durations at average output powers in excess of 1W have been demonstrated \cite{Brunner_diode_pumped,Courjaud_high_power,Major_femtosecond_2006,Holtom_mode_locked_2006} and are now available commercially \cite{website_amplitude,website_solar}.
Such lasers have used dichroic mirrors \cite{Brunner_diode_pumped,Major_femtosecond_2006,Paunescu_diode_2004,Major_extended_2006}, polarization-coupling \cite{Holtom_mode_locked_2006}, or more complex optical geometries (e.g., thin disk lasers \cite{website_amplitude,Brunner_pulses_2002}) to pump the laser crystal in an efficient manner.

@@

%TODO is this first sentance correct or should I use "I" voice?
In this chapter, a high-power, femtosecond Yb:KGW oscillator is presented that also accesses the broader emission bandwidth parallel to the optical $N_p$-axis (parallel to the crystallographic $b$-axis), yet employs a simpler geometry for polarized diode-pumping on the strongest 980nm absorption line parallel to the optical $N_m$-axis (rotated by $\sim\,20^\circ$ from the crystallographic $a$-axis \cite{Biswal_thermo_optical_05,mochalov_laser_1997,pujol_crystalline_1999}).
The laser head design is based on the thermal lens shaping (TLS) technique developed in-house for astigmatism compensation in diode-pumped Nd-doped lasers with Brewster-cut gain media \cite{Rimington_thermal_lens_2004}.
It employs a simple single layer \ce{SiO2} anti-reflection coating on the gain medium to provide minimal loss for $p$-polarized intracavity 1040nm laser radiation and less than 0.5\% surface reflection for orthogonal $s$-polarized 980nm pump light.
The result is a simple and robust, soliton mode-locked and directly diode-pumped, solid-state laser oscillator delivering over 4W of average output power in a 63MHz train of pulses with a duration less than 300fs.
Frequency doubling of this laser output in a 2mm Brewster-cut Lithium triborate (LBO) crystal provides 1.65W of average power at 520nm.
